\section*{The assignment}

You should design the architecture for a digital post service.
This means a high-level sketch of a protocol, the outline of the app internals 
and the server-side API\@.

The app should provide the following features:
\begin{enumerate}
  \item A user can register for a post box.
    As this post service will replace physical mail, it must be tied to a real 
    identity.

  \item The owner can read the mail.
    Only the owner should be able to do this --- no one else, not even service 
    staff!

  \item A sender should be able to send mail to a recipient.
    This mail should not be readable by any intermediary.

  \item Anonymous mail.
    A sender can send a letter to a recipient, but neither the recipient nor 
    the service will learn the identity of the sender.
    The service will not learn the recipient either.
\end{enumerate}
You can see the last one as optional for a higher grade.

Solving this assignment will touch upon almost every topic in the course.
Make sure to base your designs on the theory of the course, add references, 
that will help you (remember that's a part of the grading criteria).
\enquote{This feels secure} is not a convincing argument.
Likewise, \enquote{all connections should use TLS} will not cut it either; why 
do you want TLS, what properties do you need and which of those will TLS 
provide and why?
The same applies for BankID, what properties are you after?
How does BankID provide those and what are the limitations?

